### 2023-03-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
fixing broken link

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the same model as~\citet{liu-mar-li-vee-low2017}
and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the
Helfrich energy, line tension, and phase energy. The phase and bending
energies are coupled through the bending modulus. In particular, the
individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \\
  E_t &= \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
$f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local
minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature,
$\ss$ is the tangent vector, and $s$ is the arclength. We have adopted
the same setup as~\citet{soh-se-li-voi-low2010} where $\epsilon \ll 1$
ios a dimensionless parameter that controls the size of the transition
region of $u$, and $a$ is the dimensional line tension scaled by
$b_{\max}/L$. Both $\epsilon$ and $a$ are kept constant in all
simulations. The resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
\end{align}

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass. To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
\begin{align}
    b(u) = (1-u) + \beta u.
    \label{eqn:linearBending}
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (\beta+1)^{-1}$, and such values of $u$ are possible when
$\beta$ is small and the vesicle is confined to a narrow region.
Therefore, in this work we parameterize the bending modulus as
\begin{align}
    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
           \frac{\beta + 1}{2}.
    \label{eqn:tanhBending}
\end{align}
\begin{figure}[H]
  \centering
  \input{figures/concModels.tikz}
  \caption{\label{fig:concModels} \small The linear bending model in red
  (equation~\eqref{eqn:linearBending}) and the the new hyperbolic
  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
  [0,1]$.}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constitutive equations}
Using the same model as~\citet{liu-mar-li-vee-low2017}
and~\citet{soh-tse-li-voi-low2010}, the membrane forces depend on the
Helfrich energy, line tension, and phase energy. The phase and bending
energies are coupled through the bending modulus. In particular, the
individual energies are
\begin{align}
  E_b &= \frac{1}{2}\int_{\gamma} b(u) \kappa^2 \, ds, \\
  E_t &= \int_{\gamma} \sigma \, ds, \\
  E_p &= \frac{a}{\epsilon}\int_{\gamma}\left(
  f(u) +\frac{\epsilon^2}{2}|\nabla_\gamma u|^2\right) \, ds,
  \label{eqn:PhaseEnergy}
\end{align}
where $u$ is the dimensionless lipid concentration, $b(u)$ is the
lipid-dependent bending modulus, $\sigma$ is the vesicle's tension, and
$f(u) = \frac{1}{4}u^2(1-u)^2$ is the double-well potential with local
minimums at $u=0$ and $u=1$. Here, $\kappa$ is the membrane curvature,
$\ss$ is the tangent vector, and $s$ is the arclength. We have adopted
the same setup as~\citet{soh-tse-li-voi-low2010} where $\epsilon \ll 1$
is a dimensionless parameter that controls the size of the transition
region of $u$, and $a$ is the dimensional line tension scaled by
$b_{\max}/L$. Both $\epsilon$ and $a$ are kept constant in all
simulations. The resulting membrane forces are
\begin{align}
  \ff_b &= -(b(u)\kappa \nn)_{ss} -\frac{3}{2}
    \left(b(u) \kappa^2 \ss\right)_s, \\
  \ff_t &= (\sigma \ss)_s, \\
  \ff_p &= \left(\frac{a}{\epsilon}\left(f(u) -
     \frac{\epsilon^2}{2} u_s^2\right) \ss \right)_s.
\end{align}

The lipid species $u$ is governed by a fourth-order Cahn-Hilliard equation that results in the lipids phase separating while conserving their total mass. To model the variable bending, \citet{soh-tse-li-voi-low2010} propose parameterizing the bending modulus as
\begin{align}
    b(u) = (1-u) + \beta u.
    \label{eqn:linearBending}
\end{align}
However, since the double-well potential does not have hard walls, the
lipid concentration is not guaranteed to be confined to the interval
$[0,1]$. This is problematic when $u > 1$ since this results in $b(u) <
0$ if $u > (1 - \beta)^{-1}$, and such values of $u$ are possible when
$\beta$ is small and the vesicle is confined to a narrow region.
Therefore, in this work we parameterize the bending modulus as
\begin{align}
    b(u) = \frac{\beta-1}{2} \tanh\left(3\left(u-\frac{1}{2} \right)\right) + 
           \frac{\beta + 1}{2}.
    \label{eqn:tanhBending}
\end{align}
\begin{figure}[H]
  \centering
  \input{figures/concModels.tikz}
  \caption{\label{fig:concModels} \small The linear bending model in red
  (equation~\eqref{eqn:linearBending}) and the the new hyperbolic
  bending model in blue (equation~\eqref{eqn:tanhBending}). Note that
  the new bending model satisfies $b \in (\beta,1)$ even if $u \notin
  [0,1]$.}
\end{figure}
